Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-01 ms/SI.Rmd
Subset traits to ferns only, add NMDS plot

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined"
),
cache = ja_fern_cache)

@@

>>>>

loadd(list = c(
  "occ_point_data_ferns",
  "ses_phy_ferns",
  "ses_phy_ferns_endemic",
  "ses_traits_ferns",
  "shape_ferns",
  "k_taxonomy",
  "k_phylogeny",
  "regions_taxonomy",
  "regions_phylogeny",
  "species_motifs_ferns",
  "species_motifs_ferns_combined",
  "traits_nmds",
  "ppgi"
),
cache = ja_fern_cache)

@@

```{r trait-space, fig.width = 8, fig.height = 8}
# Extract points, join to PPGI
nmds_points <- traits_nmds[["points"]] %>%
  as.data.frame %>%
  rownames_to_column("taxon") %>%
  as_tibble %>%
  mutate(genus = str_split(taxon, "_") %>% map_chr(1)) %>%
  left_join(ppgi, by = "genus") %>%
  mutate(
    order = factor(order),
    family = factor(family))

# A: all ferns
a <- ggplot(nmds_points, aes(x = MDS1, y = MDS2, color = order, shape = order)) +
  geom_point() +
  scale_shape_manual(values = 1:n_distinct(nmds_points$order)) +
  labs(title = "A. Ferns")

# B: Polypods only
nmds_points_polypod <- filter(nmds_points, order == "Polypodiales")

b <- ggplot(nmds_points_polypod, aes(x = MDS1, y = MDS2, color = family, shape = family)) +
  geom_point() +
  scale_shape_manual(values = 1:n_distinct(nmds_points_polypod$family)) +
  labs(title = "B. Polypodiales") +
  guides(
    color = guide_legend(ncol = 2),
    shape = guide_legend(ncol = 2))

a + b + 
  plot_layout(nrow = 2)

ggsave(result_file("traits-nmds", "pdf"), width = 8, height = 8, units = "in")
```

**`r s_figure("traits-nmds")`**. `r s_figure_cap("traits-nmds")` Interspecific trait distances calculated using Gower's method with 16 traits, then projected into trait space using nonmetric multidimensional scaling (NMDS). **A**, All ferns. **B**, Polypodiales. Taxonomy follows PPGI.
